Git Learning Notes

### 2014-02-16 foo.tex
git lynda

>>>>

git clean % remove untracked files

navigating commit tree
tree-ish

parent commit: HEAD^, HEAD~1, HEAD~2,

git ls-tree master or HEAD %list commit tree

git log --oneline 
git log --author=""
git log --since=
git log --graph --all --decorate --oneline

git show SHA

git diff HEAD~3..HEAD % -b ignore space changes,

%use branch to try new ideas, and isolate features
compare branches
git diff --color-words master..develop

git branch --merged % to see if current branch include previous contents

rename branches:

git branch -m develop newname

git merge --no-ff branch % no fast-forward merge

true merge  %recursive strategy

resolving conflicts: 
abort: git merge --abort
manually: 
merge tool:

stashing: store temporally 
git stash save ""
git stash list 
git stash show -p stash@{0}
git stash apply or pop stash@{0}% pop, no longer in drawer, apply, make a copy from the drawer

git stash drop stash@{0} 
git stash clear % clear all stashes

% remotes 
git push -u %
